Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-02 Dissertation/Thesis/tex/ae3Dsimple.tex
updated figs of chap 5

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=1.5\textwidth]{gazebo_view.png}
        		\caption{Environment}
		\label{fig:Sim2ProjMapsGazebo}
    	\end{subfigure}
		\hspace*{0.05cm}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {3.6cm 17cm 52.5cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Collision Map}
		\label{fig:Sim2ProjMapsCollision}
    	\end{subfigure}
	\hspace*{0.1cm}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {18cm 17cm 38.1cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Entropy Map}
		\label{fig:Sim2ProjMapsEntropy}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated Environment and 2D Projected Maps at $4$ min}
	\medskip
	\small
	The robot hovering near the beginning of the simulation is shown in Figure \ref{fig:Sim2ProjMapsGazebo}. The projected maps for collision (Figure \ref{fig:Sim2ProjMapsCollision}) and entropy (Figure \ref{fig:Sim2ProjMapsEntropy}) are shown $4$ minutes into the simulation. The robot and candidates are shown the same as Figure \ref{fig:sim3DMap}, where the space is considered mostly collision-free, though still largely uncertain.
\label{fig:sim2Dmaps}
\end{figure}

>>>>

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=1.5\textwidth]{gazebo_view.png}
        		\caption{Environment}
		\label{fig:Sim2ProjMapsGazebo}
    	\end{subfigure}
		\hspace*{0.05cm}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {3.6cm 17cm 52.5cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Collision Map}
		\label{fig:Sim2ProjMapsCollision}
    	\end{subfigure}
	\hspace*{0.1cm}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {18cm 17cm 38.1cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Entropy Map}
		\label{fig:Sim2ProjMapsEntropy}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated Environment and 2D Projected Maps at $4$ min}
	\medskip
	\small
	The robot hovering near the beginning of the simulation is shown in (a). The projected maps for collision (b) and entropy (c) are shown $4$ minutes into the simulation. The robot and candidates are shown the same as Figure \ref{fig:sim3DMap}, where the space is considered mostly collision-free, though still largely uncertain.
\label{fig:sim2Dmaps}
\end{figure}

### 2018-07-02 Dissertation/Thesis/tex/multivehicle.tex
updated figs of chap 5

This chapter covers a bidding-based formulation for multiple vehicles cooperating together in the context of autonomous exploration and patrol. We focus on a series of auctions to assign tasks, and consider dynamic obstacles, such as people, in large office-like environments using a receding-horizon framework.

@@

	\begin{figure}
		\centering{
			\includegraphics[width=0.9\columnwidth]{NonZeroBump.pdf}
		}
		\caption{The bump function is designed to promote travel distances close to $d_\text{opt}$ by multiplying this function by the expected information gain objective. Travel distances less than $d_\text{opt}$ are below the robot capabilities. Travel distances beyond $d_\text{opt}$ are beyond what the robot can reach within the minimum exploration computation time.}
		\label{fig:nonzeroBumpFun}
	\end{figure}

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{SEH_cropped.png}
        		\caption{Floor Plan}
    	\end{subfigure}
	\hspace*{0.1\textwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{gazeboSEH.png}
        		\caption{Gazebo Model}
    	\end{subfigure}
	\caption{The SEH second floor plan (about $15,000$ sqft) is reconstructed with a Gazebo simulation environment.}
	\label{fig:SEHEnvironment}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{3D Occupancy Grid Map of SEH Second Floor}
	\label{fig:sim3DMap}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map of SEH Second Floor}
	\label{fig:sim2Dmaps}
\end{figure}

@@

	\begin{figure}
		\centering{
			\includegraphics[width=0.9\columnwidth]{multi_H.pdf}
		}
		\caption{Total 3D Map Cell Entropy}
		\label{fig:simH}
	\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{DegradeExamples.pdf}
\caption{The rate at which probabilities converge toward $P_\infty=0.4$ increases based on the difference magnitude of their initial values.}
\label{fig:DegradeExamples}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 3D occupancy grid map representation of the SEH second floor is shown during patrol. The robots generate these maps while avoiding collisions with each other, the environment, and a non-cooperative human.}
	\label{fig:Sim3DMapPatrol}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 2D projected map from of the SEH second floor shows degradation while robots patrol the space. The robots evade the non-cooperative human walking in a rectangular pattern, occasionally capturing the temporarily-occupied space and identifying these cells as occupied on the grid.}
	\label{fig:Sim2DMapPatrol}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{entropy_patrol_9minSwitch.pdf}
\caption{Total map entropies are tracked for separate trials: patrol of the building for $15$ minutes (blue) and patrol of the building for $9$ minutes, then hover (red). Even though the map is fairly well-known after $9$ minutes in either case, the continuous effort of patrolling over the complete time period shows lower map uncertainty beyond this time as cells are constantly degrading.}
\label{fig:DegradeExamples}
\end{figure}

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_15sec.jpg}
        		\caption{$15$ sec}
    	\end{subfigure}
	\hspace*{0.02\textwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_16sec.jpg}
        		\caption{$16$ sec}
    	\end{subfigure}
	\hspace*{0.02\textwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_17sec.jpg}
        		\caption{$17$ sec}
    	\end{subfigure}
	\caption{A cooperating robot must evade a non-cooperative human. The receding horizon framework allows a quickly-updating map to modify the exploration commands to avoid collisions with a dynamic obstacle.}
	\label{fig:EvadeHuman}
\end{figure}

>>>>

This chapter covers a bidding-based formulation for multiple vehicles cooperating together in the context of autonomous exploration and patrol. We focus on a series of auctions to assign tasks, and consider dynamic obstacles, such as people, in large office-like environments using a receding horizon framework.

@@

	\begin{figure}
		\centering{
			\includegraphics[width=0.9\columnwidth]{NonZeroBump.pdf}
		}
		\caption{Bump Function for Multi-Vehicle Autonomous Exploration}
		\medskip
		\small
		The bump function is designed to promote travel distances close to $d_\text{opt}$ by multiplying this function by the expected information gain objective. Travel distances less than $d_\text{opt}$ are below the robot capabilities. Travel distances beyond $d_\text{opt}$ are beyond what the robot can reach within the minimum exploration computation time.
		\label{fig:nonzeroBumpFun}
	\end{figure}

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{SEH_cropped.png}
        		\caption{Floor Plan}
    	\end{subfigure}
	\hspace*{0.1\textwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{gazeboSEH.png}
        		\caption{Gazebo Model}
    	\end{subfigure}
	\caption{SEH Floor Plan}
	\medskip
	\small
	The SEH second floor plan (about $15,000$ sqft) is reconstructed with a Gazebo simulation environment, excluding some small details and features of closed rooms.
	\label{fig:SEHEnvironment}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{3D Occupancy Grid Map of SEH Second Floor During Multi-Vehicle Exploration}
	\medskip
	\small
	The 3D occupancy grid map of SEH is generated from three robots coordinating their exploration strategy with auctions.
	\label{fig:sim3DMap}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map of SEH Second Floor During Multi-Vehicle Exploration}
	\medskip
	\small
	The 2D projected map serves for both entropy and collision information at the exploration height for all three vehicles as they coordinate their mapping efforts with bidding-based multi-vehicle autonomous exploration.
	\label{fig:sim2Dmaps}
\end{figure}

@@

	\begin{figure}
		\centering{
			\includegraphics[width=0.9\columnwidth]{multi_H.pdf}
		}
		\caption{Total 3D Map Cell Entropy for Multi-Vehicle Exploration}
		\medskip
		\small
		The total map cell entropy is calculated using the difference in map entropy before and after each measurement scan from each of the three coordinating vehicles.
		\label{fig:simH}
	\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{DegradeExamples.pdf}
	\caption{Grid Cell Degradation Illustration}
	\medskip
	\small
	The rate at which probabilities converge toward $P_\infty=0.4$ increases based on the difference magnitude of their initial values.
	\label{fig:DegradeExamples}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{3D Occupancy Grid Map of SEH Second Floor During Multi-Vehicle Patrol}
	\medskip
	\small
	The 3D occupancy grid map representation of the SEH second floor is shown during patrol. The robots generate these maps while avoiding collisions with each other, the environment, and a non-cooperative human.
	\label{fig:Sim3DMapPatrol}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map of SEH Second Floor During Multi-Vehicle Patrol}
	\medskip
	\small
	The 2D projected map from of the SEH second floor shows degradation while robots patrol the space. The robots evade the non-cooperative human walking in a rectangular pattern, occasionally capturing the temporarily-occupied space and identifying these cells as occupied on the grid.
	\label{fig:Sim2DMapPatrol}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{entropy_patrol_9minSwitch.pdf}
	\caption{Total 3D Map Cell Entropy for Multi-Vehicle Patrol}
	\medskip
	\small
	Total map entropies are tracked for separate trials: patrol of the building for $15$ minutes (blue) and patrol of the building for $9$ minutes, then hover (red). Even though the map is fairly well-known after $9$ minutes in either case, the continuous effort of patrolling over the complete time period shows lower map uncertainty beyond this time as cells are constantly degrading.
	\label{fig:DegradeExamples}
\end{figure}

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_15sec.jpg}
        		\caption{$15$ sec}
    	\end{subfigure}
	\hspace*{0.02\textwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_16sec.jpg}
        		\caption{$16$ sec}
    	\end{subfigure}
	\hspace*{0.02\textwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_17sec.jpg}
        		\caption{$17$ sec}
    	\end{subfigure}
	\caption{Human Collision-Avoidance Using a Receding Horizon}
	\medskip
	\small
	A cooperating robot must evade a non-cooperative human. The receding horizon framework allows a quickly-updating map to modify the exploration commands to avoid collisions with a dynamic obstacle.
	\label{fig:EvadeHuman}
\end{figure}
